\documentclass[notas.tex]{subfiles} 				%tamanho das paginas: a4

\begin{document}
\section{Conclusions and further work}\label{sec_conclusion}
For single particle states and integer quantum Hall states, complex-time evolution does not significantly alter the wave function structure in the examples considered here. Indeed, after normalization, $e^{-s\q{H}}$ acts as the identity. In accordance with \remref{rem_gcst_interpretation}, this means that the change of the wave function as the surface is deformed corresponds to a direct lift of the classical evolution. 

In the case of fractional quantum Hall states, however, while the action of $e^{s\prq{H}}$ is similar to that in the case of integer quantum Hall states, the action of $e^{-s\q{H}}$ is no longer trivial due to the powers $m$ appearing in the holomorphic factor. This action leads to changes in the structure of the wave function. This difference might be reflecting the Coulomb interaction among electrons, which one must take into account in fractional quantum Hall systems and which is being affected by the deformation of the surface.

Note that, while the unevolved wave functions have zeros of order $m$ when the position of exactly two particles coincide, the change of structure just discussed alters this substantially. This also happens in \cite{qiu_model_2012} (see Fig. 1 and the discussion following it), which contradicts (2) of Definition 2 of \cite{klevtsov_laughlin_2019}, which demands that this property is kept for all geometries. 

As for quasiholes, there is effectively a change in their position depending on the deformation parameter $s$. 

There is an interesting phenomenon arising when one takes the limit $s \to \infty$. For instance, in the case of the cylinder, the wave functions approximate distributional states concentrated around the Bohr-Sommerfeld leaves $u = 2 \pi m$. 

Mathematically, the justification for the use of GCSTs comes from the fact that these transforms are unitary in some particular cases (see \cite{kirwin_complex_2013}) and asymptotically unitary for more general cases (see \thmref{thm_gcst_asymp_unitarity}). The use of complex Hamiltonian flows to deform the surface comes from the fact that, for $\tau = is, s \in \reals^+$, they yield geodesics in the space of Kähler metrics (see \thmref{thm_complex_flow_geodesics}).

Overall, the approach presented here has the advantage of being able to make theoretical predictions for arbitrarily big deformations of the surface, corresponding to the parameter $s$. This contrasts with the perturbative techniques used e.g. in \cite{johri_probing_2016}, where the deformation must be very small. 

Further work is needed to apply these techniques to different geometies eg. the sphere and the torus. An attempt to do so for the case of the torus was made; however, fully quantizing the Hamiltonian as in \remref{rem_full_quantization} turned out to be difficult. A possible solution may be to use Berezin-Toeplitz quantization.
\end{document}